This is an example of article title

### 2024-05-17 paper/paper.tex
Minor changes
Update paper.tex

%- General peridynamics context
Peridynamics is a nonlocal continuum mechanics formulation, which was invented by Silling \cite{Silling2000}.
It has gained increased popularity as an approach for modeling fracture.
The material behavior is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.

@@

%=== What is the purpose of Peridynamics.jl? ===%
The primary purpose of the package is to provide a framework for peridynamic simulations for a broad user base.
Peridynamics simulations can be conducted with custom geometry and setup with just a few lines of code.
Due to Julia's multiple dispatch functionality, custom material models can be defined to extend the package.
Therefore, researchers can use the package to develop new peridynamic material models, simplifying their workflow by utilizing the Julia ecosystem.

>>>>

%- General peridynamics context
Peridynamics is a nonlocal continuum mechanics formulation, which was introduced by Silling \cite{Silling2000}.
It has gained increased popularity as an approach for modeling fracture.
The material behavior is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.

@@

%=== What is the purpose of Peridynamics.jl? ===%
The primary purpose of the package is to provide a framework for peridynamic simulations for a broad user base.
A user-friendly interface makes it possible to define geometries and boundary conditions with just a few lines of code.
Due to Julia's multiple dispatch functionality, custom material models can be defined to extend the package.
Therefore, researchers can use the package to develop new peridynamic material models, simplifying their workflow by utilizing the Julia ecosystem.
